Gradual Soundness: Lessons from Static Python

### 2022-01-15 pj-7.1/paper.tex
italic correction must go inside the italics, otherwise it doesn't correct anything

Like most gradual languages, \SP{} includes a dynamic type
that allows untyped expressions within a statically-typed context.
Whenever an expression or variable lacks a type annotation, \SP{} uses the
dynamic type as a default and skips most \emph{but not all}\/ static checks.
Programmers can thus add annotations to part of a module
while leaving the rest unannotated.

>>>>

Like most gradual languages, \SP{} includes a dynamic type
that allows untyped expressions within a statically-typed context.
Whenever an expression or variable lacks a type annotation, \SP{} uses the
dynamic type as a default and skips most \emph{but not all\/} static checks.
Programmers can thus add annotations to part of a module
while leaving the rest unannotated.
